---
title: "Data Validation"
---

```{r setup, include=FALSE}
source(here::here("_common.R"))
```

## Data Loading

Data are loaded by `_common.R` at book startup via `prepare_all_data()`. This Chapter verifies the loaded datasets and documents sample characteristics.

### File Checksum {#sec-checksums-validation}

The MD5 checksum uniquely identifies the data file used in this analysis. Verify against the value in the [Introduction](index.qmd#sec-checksums) and against any independently downloaded copy.

```{r checksums}
data.frame(
  File    = "rousse-cc-survey-2024.csv",
  MD5     = md5_data,
  Rows    = nrow(survey_all),
  Columns = ncol(survey_all)
) |> knitr::kable(caption = "Data File Identification and Dimensions")
```

---

## Sample Dimensions

```{r dimensions}
data.frame(
  Dataset = c("Full dataset", "A/B/C view", "A/B1/C view"),
  N       = c(nrow(survey_all), nrow(survey_data), nrow(survey_data_eu)),
  Columns = c(ncol(survey_all), ncol(survey_data), ncol(survey_data_eu)),
  Used_for = c("All groups (A, B, B1, C)", "PD, PU, CA, LS, WN, FS", "EU only")
) |> knitr::kable(caption = "Dataset Dimensions")
```

---

## Group Composition {#sec-group-composition}

```{r}
#| label: tbl-group-all
#| tbl-cap: "Group Composition — Full Dataset (rousse-cc-survey-2024.csv)"

dplyr::count(survey_all, GROUP) |>
  dplyr::rename(N = n) |>
  dplyr::mutate(Pct = round(100 * N / sum(N), 1)) |>
  knitr::kable()
```

```{r}
#| label: tbl-group-views
#| tbl-cap: "Analysis Views Derived from the Full Dataset"

data.frame(
  View = c("survey_data (A/B/C)", "survey_data_eu (A/B1/C)"),
  N    = c(nrow(survey_data), nrow(survey_data_eu)),
  Used_for = c("PD, PU, CA, LS, WN, FS", "EU only")
) |> knitr::kable()
```

---

## Sample Characteristics {#sec-demographics}

Descriptive statistics for the five demographic covariates (Age, Income, Education, Gender, Race) are reported in the covariate balance tests in [Chapter 4 (Randomization Check)](04-randomization.qmd), and the full sample-vs.-population comparison is in [Chapter 5 (Sample v. Population Analysis)](05-population.qmd).

---

## Data Quality {#sec-data-quality}

### Scenario Variables — Missing Value Report

```{r}
#| label: tbl-quality-scenario
#| tbl-cap: "Missing Value Report for Scenario Variables (Q1–Q4 and Delta)"

scenario_vars <- c(
  paste0(rep(c("PD", "PU", "EU", "CA", "LS", "WN", "FS"), each = 5),
         c("1", "2", "3", "4", "25"))
)
scenario_vars_present <- scenario_vars[scenario_vars %in% names(survey_data)]

quality_report <- check_data_quality(survey_data, columns = scenario_vars_present)
knitr::kable(quality_report)
```

### Overall Missing Data Summary

```{r quality-overall}
n_vars   <- length(scenario_vars_present)
n_perfect <- sum(quality_report$Missing_Count == 0)
n_good    <- sum(quality_report$Quality %in% c("Perfect", "Good"))

cat("Scenario variables checked: ", n_vars, "\n")
cat("Variables with zero missing: ", n_perfect, "\n")
cat("Variables with 'Perfect' or 'Good' quality: ", n_good, "\n")
```

---

## Delta Variables {#sec-delta-validation}

Delta variables (`Δ` = `Q2` − `Q3`) are created during data preparation by `create_all_deltas()`. They represent the gap between what respondents believe the law says (`Q2`) and what they believe it should say (`Q3`).

| `Δ` Value | Interpretation |
|---------|----------------|
| Positive | Law perceived as more strict than preferred |
| Zero | Perceived law matches preferred rule |
| Negative | Law perceived as more lenient than preferred |

```{r delta-validation}
delta_vars <- paste0(c("PD", "PU", "EU", "CA", "LS", "WN", "FS"), "25")
delta_present <- delta_vars[delta_vars %in% names(survey_data)]

cat("Delta variables present: ", paste(delta_present, collapse = ", "), "\n")
cat("Count: ", length(delta_present), "of 7\n")

# Quick sanity check: verify delta = Q2 - Q3
for (sc in c("PD", "PU", "CA", "LS", "WN", "FS")) {
  q2  <- paste0(sc, "2")
  q3  <- paste0(sc, "3")
  d25 <- paste0(sc, "25")
  if (all(c(q2, q3, d25) %in% names(survey_data))) {
    computed <- survey_data[[q2]] - survey_data[[q3]]
    match <- all(computed == survey_data[[d25]], na.rm = TRUE)
    cat(sprintf("  %s: Q2 - Q3 == Delta? %s\n", sc, ifelse(match, "✓", "✗ MISMATCH")))
  }
}
```
